%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% CV-LuaLaTeX en ESPAÑOL
%% Carla Cisternas
%% https://github.com/carlacisternasg/CV-LuaLaTeX

%% Based on the Awesome CV LaTeX Template
%% https://github.com/darwiin/awesome-neue-latex-cv
%% and the Bastián Gozález-Bustamante's CV-LaTeX Template
%% https://github.com/bgonzalezbustamante/CV-LaTeX

%% Creative Commons Attribution 4.0 International License
%% https://github.com/carlacisternasg/CV-LuaLaTeX/blob/master/LICENSE.md

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sectionTitle{Presentaciones en conferencias relevantes}{\faTasks}

\begin{publications}

\publicationentry{SLAS}{González-Bustamante, B., \& {\bfseries Cisternas, C.} (2022). {\itshape Seniority and Cosponsorship in the Chilean Lower House 2006-2018}. Presentation delivered at the Society of Latin American Studies Latin America Annual Conference, Bath, UK.}\\

\publicationentry{IPSA}{{\bfseries Cisternas, C.}, \& González-Bustamante, B. (2021). {\itshape Political Careers and Cosponsorship in the Chilean Lower House 2006-2018}. Presentation delivered at the XXVI World Congress of the Political Science, Online.}\\
	
\publicationentry{LASA}{{\bfseries Cisternas, C.} (2019). {\itshape Producción de leyes y copatrocinio legislativo en la Cámara de Diputados (2010-2018)}. Ponencia presentada en el XXXVII Congreso Internacional de la Asociación de Estudios Latinoamericanos, Boston, Estados Unidos.}\\

\publicationentry{USACH}{González-Bustamante, B., \& {\bfseries Cisternas, C.} (2018). {\itshape Social Network Analysis: Application for Elites Study}. Ponencia presentada en el Simposio Élites Político-Administrativas: Delineando una Agenda de Investigación, Santiago, Chile.}\\

\publicationentry{ACCP}{{\bfseries Cisternas, C.}, \& Vásquez, J. (2016). {\itshape El rol de las Comisiones Asesoras Presidenciales (2006-2014)}. Ponencia presentada en el XII Congreso Chileno de Ciencia Política, Pucón, Chile.}\\

\publicationentry{CLAD}{Barría, D., González-Bustamante, B., \& {\bfseries Cisternas, C.} (2016). {\itshape Open Government in Latin America and Spain: Analysis of the Scientific Production in Spanish}. Ponencia presentada en el XXI Congreso Internacional del CLAD sobre la Reforma del Estado y de la Administración Pública, Santiago, Chile.}\\

\publicationentry{PreALAS}{{\bfseries Cisternas, C.}, González-Bustamante, B., \& Barría, D. (2016). {\itshape Analysis of the Scientific Production in Spanish on Public Administration and Public Policies (2010-2012)}. Ponencia presentada en IX Congreso Chileno de Sociología, Talca, Chile.}\\
		
\publicationentry{PreALAS}{González-Bustamante, B., \& {\bfseries Cisternas, C.} (2016). {\itshape Co-Authorship Networks of the Political Science in Spanish (2010-2015)}. Ponencia presentada en IX Congreso Chileno de Sociología, Talca, Chile.}\\
		
\publicationentry{UBO}{{\bfseries Cisternas, C.}, \& González-Bustamante, B. (2016). {\itshape The CIEPLAN Monks: Intellectual Production and Co-Citation Networks During the Eighties}. Ponencia presentada en el Seminario Internacional Ciencias Sociales en la Encrucijada: Intelectuales y Tecnócratas Latinoamericanos en Tiempos de Autoritarismo, Santiago, Chile}\\
		
\end{publications}
\pagebreak